importE2data

### 2018-08-16 E2/analysis/importE2data.Rmd
gettting betterall the timee

Break out into target position -3, -2 etc. the targetStreamOrient

@@

for (i in 1:nrow(E)) {
  #row<- E[i,]
  #orientsThis <- row$targetStreamOrientations[[1]]
  #targetPos <- row$targetSP
  #If targetSP == NaN, it's a one-target trial and wrong side
  if (is.nan(E[i,]$targetSP)) {
    E[i,]$orientMinus3<- NaN
  } else {
    E[i,]$orientMinus3<- E[i,]$targetStreamOrientations[[1]][    E[i,]$targetSP -3    ]
    E[i,]$orientMinus2<- E[i,]$targetStreamOrientations[[1]][    E[i,]$targetSP -2    ]
    E[i,]$orientMinus1<- E[i,]$targetStreamOrientations[[1]][    E[i,]$targetSP -1    ]
    E[i,]$orient0<- E[i,]$targetStreamOrientations[[1]][    E[i,]$targetSP    ]
    E[i,]$orientPlus1<- E[i,]$targetStreamOrientations[[1]][    E[i,]$targetSP +1    ]
    E[i,]$orientPlus2<- E[i,]$targetStreamOrientations[[1]][    E[i,]$targetSP +2    ]
  }
}

>>>>

Break out into target position -3, -2 etc. the targetStreamOrient variable that contains the orientaiton of each item. This will allow seeing whether having several orientations in a row triggers the lateral bias.

@@

for (i in 1:nrow(E)) {
  #row<- E[i,]
  #orientsThis <- row$targetStreamOrientations[[1]]
  #targetPos <- row$targetSP
  #If targetSP == NaN, it's a one-target trial and wrong side
  if (is.nan(E[i,]$targetSP)) {
    E[i,]$orientMinus3 <- NaN
  } else {
    E[i,]$orientMinus4 <- E[i,]$targetStreamOrientations[[1]][    E[i,]$targetSP -4    ]
    E[i,]$orientMinus3 <- E[i,]$targetStreamOrientations[[1]][    E[i,]$targetSP -3    ]
    E[i,]$orientMinus2 <- E[i,]$targetStreamOrientations[[1]][    E[i,]$targetSP -2    ]
    E[i,]$orientMinus1 <- E[i,]$targetStreamOrientations[[1]][    E[i,]$targetSP -1    ]
    E[i,]$orient0 <- E[i,]$targetStreamOrientations[[1]][    E[i,]$targetSP    ]
    E[i,]$orientPlus1 <- E[i,]$targetStreamOrientations[[1]][    E[i,]$targetSP +1    ]
    E[i,]$orientPlus2 <- E[i,]$targetStreamOrientations[[1]][    E[i,]$targetSP +2    ]
  }
}

### 2018-08-16 E2/analysis/validateE2data.Rmd
gettting betterall the timee

Modified from importE1data.R

@@

GoogleDrivePath<-".." # to main E2 folder

#Second experiment of second backwards-letters paper. random orientation each frame.
rawDataPath<- file.path(GoogleDrivePath,
                            "Data/RawData/Data")
#raw data path containing .mat file for each subject

@@

```{r read raw data}

@@

Why is it that letterSeq is still in with all its values, but allLetterOrientations etc only has one? As you can see below, you literally can't slice

```{r}
CUall <- E[ ,E$subject=="CU" ]
i<- E$subject == "CU"
E[i,] #doens't work. You can't slice a dataframe that has a list (letterSeq) as a member, yet no error message!
subset(E, subject=="CU")
j<- En$subject == "CU"
EnCU<- En[j,]
```

@@

ALEX TO-DO
Disaggregating and thus preserving the all variables, like allLetterOrientations and allTargetORientations
Also maybe give targetSide values that make more common sense, like "dual", "left", and "right"

@@

table(one$stream,one$targetSide,one$allResponseOrientations,useNA="always")
```

>>>>

Checking some stuff out

@@

mainPath<-".." # to main E2 folder

#Second experiment of second backwards-letters paper. random orientation each frame.
rawDataPath<- file.path(mainPath,
                            "Data/RawData/Data")
#raw data path containing .mat file for each subject

@@

```{r readRawData}

@@

The below works now that turnMATintoMeltedDataframe takes care of the list elements

```{r}
#CUall <- E[ ,E$subject=="CU" ]
CUall <- E %>% filter(subject=="CU")
i<- E$subject == "CU"
E[i,] #previously didn't work. You can't slice a dataframe that has a list (letterSeq) as a member.
subset(E, subject=="CU")
j<- En$subject == "CU"
EnCU<- En[j,]
```

@@

I Disaggregated allLetterOrientations - done by importE2data.Rmd which renames it targetStreamOrientations

Also maybe give targetSide values that make more common sense, like "dual", "left", and "right"

@@

#table(one$stream,one$targetSide,one$allResponseOrientations,useNA="always")
```
